### 2020-10-21 Thesis-Chapter3-Arguments.tex
Finish section on wicked prob background

The more interesting insight is that problem definition is not self-contained. There is no way to frame the problem that
provides all the information required for a solution...

% Cite commission_tackling_2018 and some other wicked problems

@@

- rozenshtein_wicked_2018 convincingly argues the point at length

>>>>

The more important insight is one step removed: precisely because there is an inexhaustable set of potential solutions,
the problem definition---that is, the set of information required to produce a solution---is not self-contained. Each
proposed solution demands research and context to be added to the problem definition. This feedback from proposal to
definition violates the linearity of the traditional approach. One cannot reason from problem statement to proposals to
a solution; instead, one is forced to constantly refine the problem statement based on the content of proposals
themselves.

A 2018 study by the Australian government uses climate change as an example of a \ac{wicked-prob}
\cite{commission_tackling_2018}. Say the problem is initially formulated as long-term change to the environment caused
by the effects of accumulating greenhouse gasses. Responses typically take one of three broad forms: profligate behavior
in consumeristic societies must be reigned in at a local and personal level; global inter-governmental coordination is
the only solution, as individual changes will have no impact; or the situation is overblown by idealists and
power-mongers, and technological progress and adaptive markets will handle any negative effects that come to pass
\cite{commission_tackling_2018}. Which response is correct? One cannot tell from the problem statement. How much do
individual choices contribute to greenhouse gas emissions? How effective are international accords? How costly will the
changes be, and how capable is technology to respond? Evaluating the validity of each proposal requires updates to the
problem statement itself.

Elements of the problem may be tame---one can independently confirm that reducing global carbon emissions by a certain
amount will result in a certain difference in response with a certain confidence level. Combining the tame elements in a
cohesive solution is the ``wicked'' part. Despite certain tame elements, one cannot verify the effectiveness of a plan
ahead of time, port a solution from a different domain, or even definitively evaluate its performance after the fact.

@@

Dogged by concerns over privacy, security, safety, and trust, \ac{encryption} and the presupposed solution of \ac{EA} is
a \ac{wicked-prob}. It has each of the characteristics from Rittel's list above:

\begin{enumerate}
  \item There is no formulation that encapsulates the problem of encryption's interplay with privacy, security,
        safety, and trust.
  \item Balancing each value in the face of constantly evolving technology is never ending.
  \item \ac{EA} or other proposals cannot definitively solve the problem.
  \item \ac{EA} or other proposals cannot be objectively tested.
  \item Every policy implementation has irreversible impacts.
  \item There is an inexhaustable set of potential solutions to the problem.
  \item Solutions from other domains do not apply directly to this problem.
  \item The need for \ac{EA} or some alternative is a symptom of differing values, rapid technological change, and
        criminal behavior.
  \item The problem can be framed as insufficient investigatory access to digital data (presupposing \ac{EA} as the
        solution), outdated cyberlaw (presupposing legal hacking or compelled password disclosure as solutions), and
        more.
  \item The decisions of regulators and technologists alike have real impacts in the world today.
\end{enumerate}

Cybersecurity law scholar Alan Rozenshtein argues this point at length \cite{rozenshtein_wicked_2018}. He breaks the
root issues down into three categories. First, that there is disagreement on goals (or even basic premises). Sides can't
agree whether things are ``going dark'' or we're in the ``golden age of surveillance'' or how much to value competing
notions of security. Second, that information is ``uncertain and diffuse.'' There are insufficient statistics on
encryption's effect on investigations, and though the consensus is that we are not presently capable of acceptably
secure \ac{EA}, that is not certain to always be the case, especially as the area is under-researched. Third, that the
problem cannot be definitively solved. Evolving values and technology mean that the subject is always up for
renegotiation.

Rozenshtein reflects on the diagnosis positively:

\begin{displayquote}
Recognizing that something is a wicked problem is not an admission of its insolubility; rather, it’s just a realistic
appreciation of its challenges. Progress on difficult social problems reflects, almost by definition, progress on wicked
problems, whether economic inequality, environmental degradation, or government access to data. Progress can be made,
but it first requires a clear-eyed appreciation of the nature of the problem and the nature of its challenges.
\cite{rozenshtein_wicked_2018}
\end{displayquote}

Embracing reality is the first step to dealing with it \cite{baker_2019}. In the next two sections, we look at
strategies for dealing with \acp{wicked-prob}.
